\begin{center}
\begin{longtabu} to \textwidth {|
    X[4,l]|
    X[3,c]|
    X[8,l]|}
    \hline
    \textbf{Author} & \textbf{Date} & \textbf{Message} \ \hline
Amrita Mazumdar & 2014-05-11 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Amrita Mazumdar & 2014-05-11 & comments to parser \\ \hline
Neel & 2014-05-11 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Neel & 2014-05-11 & more error-handling for python stuff, pushed to src \\ \hline
Amrita Mazumdar & 2014-05-11 & some encoding fixes \\ \hline
Amrita Mazumdar & 2014-05-11 & finally got git commit history auto-adding into the paper nicely \\ \hline
Kavita Jain-Cocks & 2014-05-11 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Kavita Jain-Cocks & 2014-05-11 & added some generator comments \\ \hline
Amrita Mazumdar & 2014-05-11 & fixed some changes i made to the backtick/apostrophes \\ \hline
Kavita Jain-Cocks & 2014-05-11 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Kavita Jain-Cocks & 2014-05-11 & added some comments to generator \\ \hline
Amrita Mazumdar & 2014-05-11 & added code listings, fixed some broken paths \\ \hline
Amrita Mazumdar & 2014-05-11 & encoding issues with smart quotes, image linking, weird unicode stuff \\ \hline
Amrita Mazumdar & 2014-05-11 & encoding issues with smart quotes \\ \hline
Amrita Mazumdar & 2014-05-11 & fixed code fragment formatting \\ \hline
Neel & 2014-05-11 & some error handling for python, not pushed to run\_time yet, though, still working in py. will move to run\_time once i'm done \\ \hline
Neel & 2014-05-11 & whitepaper fixes, improved collage function \\ \hline
Neel & 2014-05-11 & finished tutorial \\ \hline
Matthew Patey & 2014-05-11 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-05-11 & Runtime. Improved how pixel objects manage color, added r,g,b fields to pixel objects. \\ \hline
Kavita Jain-Cocks & 2014-05-10 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Kavita Jain-Cocks & 2014-05-10 & added suggestions to conclusions \\ \hline
Matthew Patey & 2014-05-10 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-05-10 & Added small fix to parameter declaration rule in parser, updated tests. \\ \hline
Matthew Patey & 2014-05-10 & Updated grammar. Added LRM to paper, and added lrm and test plan sections to paper.tex. \\ \hline
Kavita Jain-Cocks & 2014-05-10 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Kavita Jain-Cocks & 2014-05-10 & commented lexer and added development environment to paper \\ \hline
Matthew Patey & 2014-05-10 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-05-10 & Paper. Some small changes in lang\_evol. Added test\_plan section. \\ \hline
Neel & 2014-05-10 & bunch of stuff for the tutorial \\ \hline
Neel & 2014-05-10 & lessons learned for neel \\ \hline
Darien Nurse & 2014-05-10 & Merge branch `master' of bitbucket-accountB:mpatey/fixel \\ \hline
Darien Nurse & 2014-05-10 & Improved error handling \\ \hline
Kavita Jain-Cocks & 2014-05-10 & added some development and runtime \\ \hline
Matthew Patey & 2014-05-10 & Removed comment token to get rid of warning. \\ \hline
Matthew Patey & 2014-05-10 & Another big reorganization. Renamed imports and directory names as needed. \\ \hline
Matthew Patey & 2014-05-10 & Fix to file name in runtime tests. \\ \hline
Darien Nurse & 2014-05-10 & Handled attribute errors in the Generator. Removed eofDedent and dedentCount warnings from lexer. \\ \hline
Matthew Patey & 2014-05-09 & Moved runtime into code so it can be tested. Added runtime tests, fixed up fixel functions. Removed blank line grammar rule. \\ \hline
Matthew Patey & 2014-05-09 & Fixed file name splitting in run\_translator and fixel scripts. Fixed forp bug. \\ \hline
Matthew Patey & 2014-05-09 & Reworked some fixel function stuff, Added a lot to runtime classes, mostly color class. \\ \hline
Matthew Patey & 2014-05-09 & Added comments to lexer, added a few forbidden words to lexer, made lexer tests error messages better. \\ \hline
Matthew Patey & 2014-05-09 & turns out leaving out the ``(object)'' in class declaration isn't shorthand, it creates old style objects (whatever those are). \\ \hline
Matthew Patey & 2014-05-09 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-05-09 & Merge branch `runtime\_image' \\ \hline
Darien Nurse & 2014-05-09 & Remove typo in lessons learned \\ \hline
Darien Nurse & 2014-05-09 & Merge branch `master' of bitbucket-accountB:mpatey/fixel \\ \hline
Darien Nurse & 2014-05-09 & added lessons learned for Darien \\ \hline
Amrita Mazumdar & 2014-05-09 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Amrita Mazumdar & 2014-05-09 & updated paths to more code \\ \hline
Kavita Jain-Cocks & 2014-05-09 & removed vin diesel \\ \hline
Matthew Patey & 2014-05-09 & Got generator to work for nested loops, still needs improvements. Wrote forp tests. \\ \hline
Matthew Patey & 2014-05-09 & First pass at forp loop. Functions for 1 loop, does not currently support nested loops. \\ \hline
Neel & 2014-05-08 & added collage function to fixelFunctions \\ \hline
Neel & 2014-05-08 & added collage function to fixelFunctions \\ \hline
Neel & 2014-05-08 & added neel's stuff for the paper \\ \hline
Neel & 2014-05-08 & fixed color function to accept text or rgb values \\ \hline
Matthew Patey & 2014-05-08 & Merge branch `runtime\_image' of bitbucket.org:mpatey/fixel into runtime\_image \\ \hline
Matthew Patey & 2014-05-08 & Fixed parser tests to handle new grammar. \\ \hline
Amrita Mazumdar & 2014-05-08 & fixed typo \\ \hline
Amrita Mazumdar & 2014-05-08 & fixed some errors in new variable parser \\ \hline
Matthew Patey & 2014-05-08 & fixed tabby spacey thing. \\ \hline
Amrita Mazumdar & 2014-05-08 & adding variable to grammar \\ \hline
Amrita Mazumdar & 2014-05-08 & more updates to grammar from bracket overloading \\ \hline
Matthew Patey & 2014-05-08 & Added some Matt paper stuff. \\ \hline
Amrita Mazumdar & 2014-05-08 & amritas lessons are ok \\ \hline
Amrita Mazumdar & 2014-05-08 & Merge branch `runtime\_image' of https://bitbucket.org/mpatey/fixel into runtime\_image \\ \hline
Matthew Patey & 2014-05-06 & added color to bif list in generator. Added better error messages to parser. Changed fixel functions to call set image data function on image objects, allowing them to null out their pixel data. \\ \hline
Matthew Patey & 2014-05-06 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-05-06 & run translator changes working directory during translation so that parsing output files always go to the same place. changes back to original before writing out files. \\ \hline
Kavita Jain-Cocks & 2014-05-06 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Kavita Jain-Cocks & 2014-05-06 & added advice for future teams to paper \\ \hline
Matthew Patey & 2014-05-06 & Merge commit `90f2d2f33a50f0d5c677a2fa6ac8232da333aad3' Bring directory changes and updated fixel script into master. \\ \hline
Matthew Patey & 2014-05-06 & Added pixel access to language. Uncommented strings in post process. Added pixel access tests. Updated not test strings to reflect changes to grammar. \\ \hline
Darien Nurse & 2014-05-06 & Merge branch `master' of bitbucket-accountB:mpatey/fixel \\ \hline
Darien Nurse & 2014-05-06 & Blocked Python keyword from Fixel \\ \hline
Kavita Jain-Cocks & 2014-05-06 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Kavita Jain-Cocks & 2014-05-06 & fixed true false so now True False in python \\ \hline
Darien Nurse & 2014-05-06 & Changed image indexes to 0 \\ \hline
Amrita Mazumdar & 2014-05-06 & added pixel access to grammar \\ \hline
Matthew Patey & 2014-05-06 & small fix \\ \hline
Matthew Patey & 2014-05-06 & Merge branch `runtime\_image' of bitbucket.org:mpatey/fixel into runtime\_image \\ \hline
Amrita Mazumdar & 2014-05-06 & rework fixelFunctions for new runtime image class \\ \hline
Matthew Patey & 2014-05-06 & small changes to fixel functions. Implemented bracket pixel access, lazy pixel data loading for image class. \\ \hline
Amrita Mazumdar & 2014-05-06 & Merge branch `runtime\_image' of https://bitbucket.org/mpatey/fixel into runtime\_image \\ \hline
Matthew Patey & 2014-05-06 & created image runtime class. \\ \hline
Amrita Mazumdar & 2014-05-06 & executable permissions on fixel \\ \hline
Matthew Patey & 2014-05-06 & Renamed some stuff so that it's a little less confusing. \\ \hline
Kavita Jain-Cocks & 2014-05-06 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Kavita Jain-Cocks & 2014-05-06 & lessons learned for Kavita \\ \hline
Matthew Patey & 2014-05-06 & changed file output to use name of input file. \\ \hline
Amrita Mazumdar & 2014-05-06 & fixed file mode issue for grayscale \\ \hline
Matthew Patey & 2014-05-06 & Changed test script to call tests on correct directory regardless of where it is called from. Changed post process to add fixel to program path so imports will work regardless of where output python is run from. caption bif now uses path to file when opening font file so it can be opened regardless of current directory. Wrote new top level python script that can be invoked directly (if python executable is in your path). By adding the top level fixel directory to your path, the script can be invoked from anywhere. \\ \hline
Matthew Patey & 2014-05-05 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-05-05 & Wrote script that translates fixel file passed as first argument and then calls it with the rest of the arguments. \\ \hline
Amrita Mazumdar & 2014-05-05 & filled in rest of concl skeleton \\ \hline
Amrita Mazumdar & 2014-05-05 & added conclusiosn to paper \\ \hline
Amrita Mazumdar & 2014-05-05 & fixed font path \\ \hline
Amrita Mazumdar & 2014-05-05 & added font \\ \hline
Matthew Patey & 2014-05-05 & updated post process to reflect changes Neel made. Added complex full fixel test. Added diff printout to fixel tests. Changed python test items to be tuple of main and rest of program to allow better testing. \\ \hline
Neel & 2014-05-04 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Neel & 2014-05-04 & added test string to file (still missing expected tree output), added support for grabbing pixel data from image \\ \hline
Amrita Mazumdar & 2014-05-04 & ADDED ASCII ART MOST IMPT TASK \\ \hline
Neel & 2014-05-04 & added support for saving color values \\ \hline
Matthew Patey & 2014-05-02 & Fixed bugs I introduced to generator. Added more necessary python to post\_process. Commented out full fixel test. Will need to address new post-processing we do. Updated generator tests to handle two strings returned by generator. Updated python tests strings to have ``ns.'' and ``fixelFunctions.'' where appropriate, and to have main after def's. Made py a package so we can import from it. Added a test fixel function. If I remember correctly we decided on .fxl, but if I got that wrong we can change it. \\ \hline
Matthew Patey & 2014-05-02 & Merge branch `generator' of bitbucket.org:mpatey/fixel into generator \\ \hline
Matthew Patey & 2014-05-02 & Added post process step that adds additional python necessary to run files. Added generator code that appends necessary things to certain expressions. Made generator indent count an instance variable. \\ \hline
Darien Nurse & 2014-05-02 & Added File I/O \\ \hline
Matthew Patey & 2014-05-02 & Added in generator test for indent. \\ \hline
Matthew Patey & 2014-05-02 & Merge branch `tests' \\ \hline
Matthew Patey & 2014-05-02 & Removed duplicate function in generator tests. \\ \hline
Matthew Patey & 2014-05-01 & Added parser test for indent. \\ \hline
Matthew Patey & 2014-05-01 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-05-01 & added better error message for trees that don't match in tests. \\ \hline
Kavita Jain-Cocks & 2014-05-01 & fix merge conflicts \\ \hline
Kavita Jain-Cocks & 2014-05-01 & added first half of generator tests \\ \hline
Amrita Mazumdar & 2014-05-01 & fixed tab spaces for one of the tests that was weird \\ \hline
Amrita Mazumdar & 2014-05-01 & added code generator tests \\ \hline
Amrita Mazumdar & 2014-05-01 & adding this awkward section with silly picture \\ \hline
Kavita Jain-Cocks & 2014-04-30 & fixed merge conflicts \\ \hline
Kavita Jain-Cocks & 2014-04-30 & fixed some spacing stuff for project plan \\ \hline
Kavita Jain-Cocks & 2014-04-30 & Merge branch `tests' of bitbucket.org:mpatey/fixel into tests \\ \hline
Kavita Jain-Cocks & 2014-04-30 & added project plan - still unfinished, need testing \\ \hline
Amrita Mazumdar & 2014-04-30 & update gitignore for macs \\ \hline
Amrita Mazumdar & 2014-04-30 & working on integrating images to paper \\ \hline
Amrita Mazumdar & 2014-04-30 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Amrita Mazumdar & 2014-04-30 & added pix 2 paper, language evolution section, etc \\ \hline
Matthew Patey & 2014-04-30 & changed generator dedent from slicing to del to avoid copying list. \\ \hline
Neel & 2014-04-28 & small changes to fix final sample python script \\ \hline
Amrita Mazumdar & 2014-04-28 & indent and dedent added to code generation, and newline procesing, yay \\ \hline
Matthew Patey & 2014-04-26 & Updated tests to improve coverage based on coverage results. Fixed two tests that were not being run because of names. \\ \hline
Matthew Patey & 2014-04-26 & Added coverage output file to ignore. \\ \hline
Matthew Patey & 2014-04-26 & Parser: fixed primary expression to token productions. Got all the parser tests working. Added fix to tree strings to handle brackets as node names. \\ \hline
Matthew Patey & 2014-04-26 & Fix to parser, got all lexer tests passing. \\ \hline
Matthew Patey & 2014-04-26 & Merge branch `tests' of bitbucket.org:mpatey/fixel into tests \\ \hline
Matthew Patey & 2014-04-26 & Fixed whitespace in grammar.txt. Added ``function\_def'' ``or\_and'' and ``not'' test source. \\ \hline
Kavita Jain-Cocks & 2014-04-26 & added some tests source strings and fixed for in parser and grammar \\ \hline
Matthew Patey & 2014-04-26 & Added util that generates list syntax token stream from source, similar to tree generation from source. Added `.' to lexer literals. Added lexer indent test. \\ \hline
Matthew Patey & 2014-04-25 & Revert ``test'' \\ \hline
Matthew Patey & 2014-04-25 & test \\ \hline
Matthew Patey & 2014-04-22 & In lexer changed leadingWhitespace\_leftmostDEDENT match beginning of line instead of consuming a newline, to avoid conflict with blank line rule. Changed for loops (and list access for consistency) to use primary instead of intermediate expressions because our function calls don't nest well (ambiguous commas). Note we support an expression surrounded by parentheses, which is considered a primary expression. Fixed assignment expression to only assign to variables, not ID's. \\ \hline
Matthew Patey & 2014-04-21 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-04-21 & Fixed tests to use new intermediate expression grammar symbol. \\ \hline
Nilkanth Patel & 2014-04-21 & Merge branch `neel' of https://bitbucket.org/mpatey/fixel \\ \hline
Nilkanth Patel & 2014-04-21 & made a sample python function to show professor aho on wednesday. generates dummy images and uses new method for function calling. \\ \hline
Matthew Patey & 2014-04-21 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-04-21 & Updated grammar text file. \\ \hline
Amrita Mazumdar & 2014-04-21 & added new rules for intermediate expression to parser \\ \hline
Amrita Mazumdar & 2014-04-21 & Added a README for clarity \\ \hline
Amrita Mazumdar & 2014-04-21 & Merge branch `master' of https://bitbucket.org/mpatey/fixel into paper \\ \hline
Matthew Patey & 2014-04-21 & Reworked generator again in preparation for INDENT/DEDENT, now each node either has custom function to process it or uses default that includes an insert spaces lookup. Our grammar was ambiguous whoops! LR parser can't tell difference between function call and function definition. Implemented a fix by removing \# from declaratoin (we can change to something else). Changed test\_utils to print repr of tree\_strings, so whitespace is printed as string representation (e.g.~show \n instead of an actual newline). \\ \hline
Matthew Patey & 2014-04-20 & Fixed error in some regex (inside {[}{]} special characters lose there meaning\ldots{}my bad!). \\ \hline
Matthew Patey & 2014-04-20 & Removed auxIndent from Lexer. If we decide we want variable indent widths, we need to use a stack. Added windows newlines to all regex's matching \n. Added rule to skip blank lines. \\ \hline
Matthew Patey & 2014-04-20 & Lexer now adds all missing DEDENT's at EOF, and discards blank lines. As result of eof behavior, files with missing \n at end of line will not be recognized. Changed tree printing to use repr so we can see whitespace. \\ \hline
Matthew Patey & 2014-04-20 & Reworked generator to use strings table and custom behavior table (both are dictionary of dictionaries). Added comma to literals in lexer. Changed ID to function so that it can check for reserved words. Indent and dedent tokens are now accompanied by identical values. Changed function\_definition and parameter\_declaration in parser (and grammar.txt) so that parameter\_declaration goes to epsilon. \\ \hline
Matthew Patey & 2014-04-20 & Added index to custom behavior in generator so it can occur after any child. Added custom behavior for function definition. Removed EOF token that I added awhile ago, but never figured out how to use it. Stopped lexer from changing the value of number tokens to int (but still checks if the conversion succeeds). Changed lots of rules in parser; parser is a representation of fixel, so I think it's best to leave all tokens in and let generator decide what to omit (e.g. `\#'), plus all tokens must be turned into new nodes. Changed oneliner tests to have newline at end. \\ \hline
Matthew Patey & 2014-04-19 & Revert ``Added test util that runs the lexer only. Works similar to tree verification where name of attribute in test\_strings is supplied (e.g.~use oneliner\_source to run lexer on that string). Output is tokens.'' \\ \hline
Matthew Patey & 2014-04-19 & Added -v option to run\_fixel script that prints each intermediate step of translation. \\ \hline
Matthew Patey & 2014-04-18 & Just kidding! turns out epsilon is not needed in parameter\_declaration because function\_definition has a production with no parameter\_declaration. Updated grammar.txt aslo. \\ \hline
Matthew Patey & 2014-04-18 & quick fix, wrote epsilon rule for parameter declaration. \\ \hline
Matthew Patey & 2014-04-18 & Added custom functions for nodes to generator. This allows function expressions to generate empty `(' `)' if it has no parameters. \\ \hline
Kavita Jain-Cocks & 2014-04-18 & allows newline when dedent starts at edge of file \\ \hline
Kavita Jain-Cocks & 2014-04-18 & Merge branch `master' into neel \\ \hline
Kavita Jain-Cocks & 2014-04-17 & remove testing from lexer \\ \hline
Matthew Patey & 2014-04-17 & Fixed last change from ( to {[} for tree strings. \\ \hline
Matthew Patey & 2014-04-17 & Merge branch `tests' of bitbucket.org:mpatey/fixel into tests \\ \hline
Matthew Patey & 2014-04-17 & Made tree strings not be ws dependent. Deleted sloppy code at end of test\_utils. Added generator tests module. \\ \hline
Darien Nurse & 2014-04-17 & Changed parenthesis to brackets in test\_utils. Changed oneliner\_tree in test\_strings to use brackets instead of parenthesis. Made a test case for comparing input fixel code to target python code. Added a tree making website to the README \\ \hline
Kavita Jain-Cocks & 2014-04-17 & lexer no longer consumes first character at start of line for no dedents \\ \hline
Matthew Patey & 2014-04-17 & Changed fixel name op main function to translate, which now takes source string as argument and returns a python string. \\ \hline
Matthew Patey & 2014-04-17 & Added test util that runs the lexer only. Works similar to tree verification where name of attribute in test\_strings is supplied (e.g.~use oneliner\_source to run lexer on that string). Output is tokens. \\ \hline
Matthew Patey & 2014-04-17 & Added multiline support to lex, allowing \^{} to be used to match beginning of line. Gave example of use in indent rule. \\ \hline
Nilkanth Patel & 2014-04-16 & small fix for lexer decent thing \\ \hline
Nilkanth Patel & 2014-04-16 & lexer is working as it should with indent/dedent! \\ \hline
Nilkanth Patel & 2014-04-16 & Merge branch `master' into neel \\ \hline
Nilkanth Patel & 2014-04-16 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Nilkanth Patel & 2014-04-16 & fix to get the lexer working again. \\ \hline
Matthew Patey & 2014-04-16 & Revert ``small changes to py functions'' \\ \hline
Nilkanth Patel & 2014-04-16 & INDENT DEDENT WORKS MOSTLY \\ \hline
Amrita Mazumdar & 2014-04-16 & Merge branch `master' of https://bitbucket.org/mpatey/fixel into paper \\ \hline
Amrita Mazumdar & 2014-04-16 & added some source code to appendix \\ \hline
Amrita Mazumdar & 2014-04-16 & added some info to lrm but this will be a more involved section \\ \hline
Amrita Mazumdar & 2014-04-16 & added cleanup to script \\ \hline
Amrita Mazumdar & 2014-04-16 & script now compiles md to tex and all tex to pdf together \\ \hline
Amrita Mazumdar & 2014-04-16 & base runscript for creating paper \\ \hline
Amrita Mazumdar & 2014-04-16 & added pdf to gitignore \\ \hline
Amrita Mazumdar & 2014-04-16 & gitignore for tex files \\ \hline
Amrita Mazumdar & 2014-04-16 & markdown files for sections completed added \\ \hline
Amrita Mazumdar & 2014-04-16 & basic tex framework \\ \hline
Nilkanth Patel & 2014-04-16 & lexer updates for indent dedent \\ \hline
Nilkanth Patel & 2014-04-16 & Merge branch `neel' of https://bitbucket.org/mpatey/fixel into neel \\ \hline
Nilkanth Patel & 2014-04-16 & small changes to py functions \\ \hline
Nilkanth Patel & 2014-04-16 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Amrita Mazumdar & 2014-04-16 & commented generator for clarity \\ \hline
Matthew Patey & 2014-04-15 & Fixed the oneliner test for the parser. \\ \hline
Matthew Patey & 2014-04-14 & stuff \\ \hline
Matthew Patey & 2014-04-14 & test! \\ \hline
Matthew Patey & 2014-04-14 & removed test.txt. \\ \hline
Matthew Patey & 2014-04-14 & testing testy test. \\ \hline
Nilkanth Patel & 2014-04-14 & Merge branch `neel' of https://bitbucket.org/mpatey/fixel \\ \hline
Nilkanth Patel & 2014-04-14 & linespace \\ \hline
Amrita Mazumdar & 2014-04-14 & fixed epsilon \\ \hline
Matthew Patey & 2014-04-14 & Fixed test. \\ \hline
Matthew Patey & 2014-04-14 & Wrote test to fail, testing out jenkins with the awesome new testing suite. \\ \hline
Matthew Patey & 2014-04-13 & Added function to print tree string for AST built from given source code. \\ \hline
Matthew Patey & 2014-04-11 & Finished parser and lexer test framework. \\ \hline
Matthew Patey & 2014-04-11 & Reorganized project so that annoying imports work. Requires having top level directory (``code'') that IS NOT a package, which contains any scripts that will be run as well as all packages. \\ \hline
Matthew Patey & 2014-04-10 & wrote script so that any string in test\_strings can be run through the pretty formatter. use -h for usage. \\ \hline
Matthew Patey & 2014-04-10 & Created test\_utils module that contains functions to be used across test modules and debugging functions. Also created simple script to run it with an example. Wrote code to create tree from string representation, prints it out with tree's repr function. Desired use is to see tree-strings in human friendly format. \\ \hline
Matthew Patey & 2014-04-10 & Worked on nodes, needs to be reworked. Wrote method to obtain string from tree. \\ \hline
Matthew Patey & 2014-04-09 & I mocked lex and got yacc to build a tree with it! \\ \hline
Matthew Patey & 2014-04-14 & Merge branch `generator' \\ \hline
Nilkanth Patel & 2014-04-14 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Amrita Mazumdar & 2014-04-14 & parser finished and working, yay \\ \hline
Amrita Mazumdar & 2014-04-14 & day 1 darien and amrita parser additions \\ \hline
Matthew Patey & 2014-04-11 & fixed typos in grammar. \\ \hline
Nilkanth Patel & 2014-04-10 & Merge branch `neel' \\ \hline
Nilkanth Patel & 2014-04-10 & small change \\ \hline
Nilkanth Patel & 2014-04-10 & added new buil-in functions \\ \hline
Matthew Patey & 2014-04-10 & Fixes to generator now that Leaf is gone. \\ \hline
Matthew Patey & 2014-04-10 & Merge branch `master' into generator \\ \hline
Matthew Patey & 2014-04-10 & Removed leaf type, now all tree nodes are of type Node. To make a leaf, simply don't pass any children arguments. \\ \hline
Matthew Patey & 2014-04-09 & turns out imports always break when running a script in a package, so made one ooutside of the package. \\ \hline
Matthew Patey & 2014-04-09 & Maybe dealt with epsilon. \\ \hline
Matthew Patey & 2014-04-09 & First pass at code generation, works for 1 liner, but leaves in \# and @. \\ \hline
Amrita Mazumdar & 2014-04-07 & added literals \\ \hline
Matthew Patey & 2014-04-07 & added more newline flexibility. \\ \hline
Matthew Patey & 2014-04-07 & tried out character literals \\ \hline
Matthew Patey & 2014-04-07 & modified git ignore and added copy of lexer modified to work with yacc. \\ \hline
Matthew Patey & 2014-04-07 & By golly it's working! Also made another fix for grammar. \\ \hline
Matthew Patey & 2014-04-07 & Added ply to the src directory. \\ \hline
Matthew Patey & 2014-04-07 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-04-07 & wrote part of parser. \\ \hline
Darien & 2014-04-06 & Darien did some parsing junk: function-def, parameter-dec, statement-list, statement \\ \hline
Matthew Patey & 2014-04-06 & Fixed grammar, started parser. \\ \hline
Matthew Patey & 2014-04-06 & Merge branch `master' of bitbucket.org:mpatey/fixel \\ \hline
Matthew Patey & 2014-04-06 & made parser.py file. \\ \hline
Amrita Mazumdar & 2014-04-06 & lexer working properly on fixel input \\ \hline
Amrita Mazumdar & 2014-04-06 & sorted out tabs \\ \hline
Amrita Mazumdar & 2014-04-06 & more to lexer \\ \hline
Matthew Patey & 2014-04-06 & Added field and list access, dealt with functions (didn't end up forbidding inlining). \\ \hline
Matthew Patey & 2014-04-06 & Added grammar file to repo. Might be useful (at least at first) to have on git. \\ \hline
Nilkanth Patel & 2014-04-05 & I think i'm doing this right? these are our sample python programs. \\ \hline
Nilkanth Patel & 2014-04-05 & Created new branch neel \\ \hline
Nilkanth Patel & 2014-04-05 & Merge branch `master' of https://bitbucket.org/mpatey/fixel \\ \hline
Amrita Mazumdar & 2014-04-05 & OUR LEXER \\ \hline
Nilkanth Patel & 2014-03-31 & Am I doing this right hope so \\ \hline
Amrita Mazumdar & 2014-03-29 & i did it yay \\ \hline
Amrita Mazumdar & 2014-03-29 & amrita is trying \\ \hline
Matthew Patey & 2014-03-04 & Okay sorry guys, should be the last jenkins test. It's gonna be awesome! \\ \hline
Matthew Patey & 2014-03-04 & jenkins test. \\ \hline
Matthew Patey & 2014-03-04 & Yay I fixed it! \\ \hline
Kavita Jain-Cocks & 2014-03-04 & Kavita broke everything. \\ \hline
Matthew Patey & 2014-03-04 & jenkins test. \\ \hline
Matthew Patey & 2014-03-04 & Changed tests.py to pass. \\ \hline
Matthew Patey & 2014-03-04 & added initial test file to test jenkins. \\ \hline
Matthew Patey & 2014-02-05 & Added a setup script. Added content to readme. \\ \hline
Matthew Patey & 2014-02-05 & Added a git ignore file. \\ \hline
Matthew Patey & 2014-02-05 & First commit, added README. \\ \hline
\end{longtabu}
\end{center}
